RTS AI: Problems and Techniques

### 2015-01-20 ECGG_RTSProblems/ECGG_RTSProblems.tex
added Dave s new figure

\begin{figure}
    \centering
    \includegraphics[width=0.7\columnwidth]{figures/levels_abstraction.pdf}
    \caption{RTS  AI  levels  of abstraction  and  theirs  properties:
      uncertainty  (coming  from  partial  observation  and  from  not
      knowing the  intentions of  the opponent)  is higher  for higher
      abstraction  levels.  Timings  on  the right  correspond  to  an
      estimate   of   the   duration   of   a   behavior   switch   in
      StarCraft. Spatial and temporal  reasoning are indicated for the
      levels at which greedy solutions are not enough.}
    \label{fig:levels-abstraction}
\end{figure}

>>>>

\begin{figure}
    \centering
%    \includegraphics[width=0.7\columnwidth]{figures/levels_abstraction.pdf}
    \includegraphics[width=0.7\columnwidth]{figures/categories}
    \caption{RTS  AI  levels  of abstraction  and  typical sub-problems associated with them:
      %uncertainty  (coming  from  partial  observation  and  from  not knowing the  intentions of  the opponent)  is higher  for higher abstraction  levels.  
      Timings correspond  to  an
      estimate   of   the   duration   of   a   behavior   switch   in
      StarCraft. %Spatial and temporal  reasoning are indicated for the levels at which greedy solutions are not enough.
      }
    \label{fig:levels-abstraction}
\end{figure}
